An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-13 EconGrowth2.Rnw

Constraints on the fitting parameters include 
$\delta_1 \in [0,1]$,
$\delta \in [0,1]$,
$\rho_1 \in [-1,0] \cup [0,\infty)$, and
$\rho \in [-1,0] \cup [0,\infty)$.

>>>>

Constraints on the fitting parameters include 
$\delta_1 \in [0,1]$,
$\delta \in [0,1]$,
$\rho_1 \in [-1,0) \cup (0,\infty)$, and
$\rho \in [-1,0) \cup (0,\infty)$.
